Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-03-02 manuscript.tex
Placeholder for the 2 analysis figures
The error x distance-size ratio curves for V, gz and gzz.
The curves for different heights for gzz.

\pdfoutput=1
%\documentclass[paper,twocolumn]{geophysics}
%\documentclass[manuscript]{geophysics}
%\documentclass[manuscript,endfloat]{geophysics}
\documentclass{article}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\newcommand{\mitbf}[1]{\mathbf{{#1}}}

% To leave comments on Overleaf
\usepackage[colorinlistoftodos]{todonotes}

@@

%\righthead{Tesseroids}
%\ms{Submission} % manuscript number

%\address{
    \noindent
    \footnotemark[1]Universidade do Estado do Rio de Janeiro,
    Rio de Janeiro, Brazil.
    email: leouieda@gmail.com
    \footnotemark[2]Observat\'orio Nacional,
    Rio de Janeiro, Brazil.
%}

@@

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in the open-source package \textit{Tesseroids}.
The software is freely available
online\footnote{
\href{http://tesseroids.leouieda.com}{http://tesseroids.leouieda.com}}
under the BSD 3-clause open-source license.
An archived version of the source code
is available as part of this article.

@@

>>>>

\pdfoutput=1
\documentclass[paper,twocolumn]{geophysics}
%\documentclass[manuscript]{geophysics}
%\documentclass[manuscript,endfloat]{geophysics}
%\documentclass[twocolumn]{article}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\newcommand{\mitbf}[1]{\mathbf{{#1}}}

% To leave comments
\usepackage[colorinlistoftodos]{todonotes}

@@

\righthead{Tesseroids}
\ms{Submission} % manuscript number

\address{
    \noindent
    \footnotemark[1]Universidade do Estado do Rio de Janeiro,
    Rio de Janeiro, Brazil.
    email: leouieda@gmail.com
    \footnotemark[2]Observat\'orio Nacional,
    Rio de Janeiro, Brazil.
}

@@

We have implemented the calculation of
the tesseroid gravitational fields
with adaptive discretization
in the open-source package \textit{Tesseroids}.
It is freely available
online through the software website\footnote{
\href{http://tesseroids.leouieda.com}{http://tesseroids.leouieda.com}}
under the BSD 3-clause open-source license.
An archived version of the source code
is available as part of this article
and online\footnote{\href{}{\todo[inline]{insert a ZENODO doi}}}.

@@

\begin{figure}
    %\centering
    %\includegraphics[width=0.4\textwidth]{figs/distance-size-curves}
    \missingfigure{}
    \caption{
        The maximum difference between the computed tesseroid and shell effects
        as a function of the distance-size ratio $D$
        for (a) the gravitational potential, (b) $g_z$, and (c) $g_{zz}$.
        The difference is given as a percentage of the shell effect.
        Curves correspond to the different tesseroid models:
        $1^\circ \times 1^\circ$ tesseroids with computation grid at
        2 km height at the polar region,
        $1^\circ \times 1^\circ$ tesseroids with computation grid at
        2 km height at the equatorial region,
        $1^\circ \times 1^\circ$ tesseroids with computation grid at
        260 km height at the polar region,
        and
        $30^\circ \times 30^\circ$ tesseroids with computation grid at
        2 km height at the polar region.
    }
    \label{fig:dist-size-curves}
\end{figure}

\begin{figure}
    %\centering
    %\includegraphics[width=0.4\textwidth]{figs/gzz-with-height}
    \missingfigure{}
    \caption{
        Variation of $g_{zz}$ difference curves for computation grids at
        varying heights.
    }
    \label{fig:gzz-with-height}
\end{figure}
